---
title: "FAS"
output: html_document
---



```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```


The first step is to read in the data.

```{r}
dat<-read.csv("Fasproject.csv")

```

The next step is to check out the structure

```{r}
str(dat)
```

I need to change the scores to numeric and subject to a factor.

```{r}
dat$scores<-as.numeric(dat$scores)
dat$subject<-as.factor(dat$subject)
str(dat)
```


2-way ANOVA between subjects to determine if there is an effect of and interactions between viewing the video and FAS scores (inital and second).

```{r}
summary(aov(scores~video*survey, data=dat))
```

There was no main effect of viewing the video upon the FAS scores, F(1) = .861, p = .362.  There was no main effect of the time of the survey upon the FAS scores, F(1) = .128,
p = .724.  There was no interaction of the viewing of the video and time of the survey upon the FAS scores,  F(1) = .012, p = .914.


Now to create a bar graph to show the means of the initial and second scores according to whether or not the subjects viewed the video.

```{r}
library(ggplot2)
library(gplots)
library(dplyr)


temp<-dat%>%group_by(video,survey)%>%
  summarize(means=mean(scores),
            sems=sd(scores)/sqrt(length(n)))

```

```{r}
f<-ggplot(temp, aes(x=video,
                    y=means,
                    fill=survey))+
  geom_bar(stat="identity",position=position_dodge())+
  scale_fill_manual(values=c("purple","darkblue"),
                     name="Survey",
                     breaks=c("initial","second"),
                     labels=c("Initial", "Second"))+
  geom_errorbar(aes(ymax=means+sems,
                    ymin=means-sems),
                width=.2,
                position=position_dodge(.9))+
  ggtitle("Mean FAS Scores")+
  labs(x="Viewed Video",y="Mean Scores")+
  theme(plot.title=element_text(size=15,face="bold",vjust=.5))+
  theme(axis.title.x=element_text(size=12,face="bold",vjust=-.25))+
  theme(axis.title.y=element_text(size=12,face="bold",vjust=1))+
  theme(axis.text.x=element_text(size=10,face="bold",color="black"))+
  theme(axis.text.y=element_text(size=10,face="bold",color="black"))+
  coord_cartesian(ylim=c(min(temp$means)-2*max(temp$sems),
                         max(temp$means)+2*max(temp$sems)))+
  theme(panel.border=element_blank(),axis.line=element_line())+
  theme(panel.grid.major.x=element_blank())+
  theme(panel.grid.major.y=element_line(color="darkgrey"))+
  theme(panel.grid.minor.y=element_blank())+
  theme(legend.position=c(.4,.8))+
  theme(legend.background=element_blank())+
  theme(legend.background=element_rect(color="black"))+
  theme(legend.title=element_blank())+
  theme(legend.title=element_text(size=12))+
  theme(legend.title.align=.5)+
  theme(legend.text=element_text(size=10,face="bold"))
f
```



